\bf{Software Complexities: Do System and Change Complexity Relate?}

### 2013-12-18 paper/paper.tex
.

\author{Aldosary, Buthainah\\
\texttt{b_aldosa@encs.concordia.ca}}
\affil{Concordia University\\
 Montreal, Canada}

@@

In figure \ref{fig:ccVstc} we illustrate a system which undergoes numerous changes. The vertical lines represent each version. During each version's development, the change complexity measures are assessed. In between versions, traditional complexity measures are computed. These are denoted by CCM and TCM respectively.

@@

\begin{equation}
{{CCM_{v(i)}} = {TCM_{v(i+1)}}-{TCM_{v(i)}}}
\end{equation}

\begin{equation}
{{TCM_{v(i+1)}} = \sum\limits_{i=0}^iCCM_{v(i)}}
\end{equation}

\begin{equation}
{{{TCM_{v(i)}} = CCM_{v(i)}}   _{n=1000}}
\end{equation}

>>>>

\author{Aldosary, Buthainah\\
\texttt{aldosa@encs.concordia.ca}}
\affil{Concordia University\\
 Montreal, Canada}

@@

In figure \ref{fig:ccVstc} we illustrate a system which undergoes numerous changes. The vertical lines represent each version. During each version's development, the change complexity measures are assessed. In between versions, traditional complexity measures are computed. These are denoted by CCM and TCM respectively. To answer our research questions, for example at version 3, we want to see if \textsc{ ccm(v3)= tcm(v4)-tcm(v3)} (\ref{eq:Eq2}), \textsc {tcm(v4)=ccm(v1)+ccm(v2)+ccm(v3)
} (\ref{eq:Eq3}), finally we want to see if \textsc {tcm(v3)=ccm(v3)} for the last 1000 commits (\ref{eq:Eq4}).

@@

\begin{equation} \label{eq:Eq2}
{{CCM_{v(i)}} = {TCM_{v(i+1)}}-{TCM_{v(i)}}}
\end{equation}

\begin{equation} \label{eq:Eq3}
{{TCM_{v(i+1)}} = \sum\limits_{i=0}^iCCM_{v(i)}}
\end{equation}

\begin{equation}  \label{eq:Eq4}
{{{TCM_{v(i)}} = CCM_{v(i)}}   _{n=1000}}
\end{equation}
